\documentclass[11pt]{article}
\setlength{\parindent}{0em}
\usepackage[margin=1in]{geometry}

\begin{document}

\begin{center}
  \textbf{\Large Milestone \#7}\\\large NetBSD Wifi Browser Project 2022\\
  Dylan Roy, Stephen Loudiana, Kevin McGrane
\end{center}

\section{General Progress Report}
Surf is finished, so work on an XLib GUI of the wifi browser has begun.
At the very moment, the GUI has some buttons and is almost successfully
listing available networks from a scan. CLI methods are correctly implemented 
with the help listing for each command, as well as the syntax to be used for 
getopt_long. Most of the work this week was researching how to use getopt_long 
for our program. The TUI is at a stage where API implementation is now needed to further implement, as of now the TUI displays placeholder networks and the user is able to select a specific network and open a sub window where they will be able to access more network specific options and commands.

\textbf{Accomplishments}
\begin{itemize}
  \item Started a GUI: Hangten
  \item Help methods for CLI, program loop fixed, exit method, reorganizing of cli
  \item Have a TUI that works and is able to be interacted with
\end{itemize}

\textbf{Targets Not Met:}
\begin{itemize}
  \item TUI has not fully implemented API
\end{itemize}


\section{Git Branch Report}

\newpage
\section{Individual Progress}

\textbf{Kevin: 7 hours, 15 minutes}
\begin{itemize}
  \item Implemented placeholder connections that are able to be selected
  \item Implemented light user input and interaction to select possible Network connection
  \item Formated window for displaying all possible network connectinos
  \item Began implementation on sub window used for network specific actions once networks is selected
  \item Brainstormed more Naming options and finalized on either "Costal" or "Tidal"
\end{itemize}

\textbf{Dylan:}
\begin{itemize}
  \item More Surf error stuff
  \item Started XLib GUI
  \item Buttons!
  \item Almost listing scanned networks
\end{itemize}

\textbf{Stephen: 4 hours, 13 minutes}
\begin{itemize}
  \item Implemented CLI methods to use getopt_long syntax
  \item Did some research on getopt_long and how to implement it
  \item Fixed help listings for each command and fixed command loop 
  \item Most of the work this week involved developing a plan to use 
	getopt_long in our program. To which I am fully confident in 
	implementing. 
\end{itemize}

\end{document}
