\documentclass[11pt]{article}
\setlength{\parindent}{0em}
\usepackage[margin=1in]{geometry}

\begin{document}

\begin{center}
  \textbf{\Large Milestone \#9}\\\large NetBSD Wifi Browser Project 2022\\
  Dylan Roy, Stephen Loudiana, Kevin McGrane
\end{center}

\section{General Progress Report}
On the front of the API, nothing needs to done before the final report.
At this point, the GUI will not be in a usable state by the final report
let alone the presentation.This is okay since this part of the project was 
a "if there's time" part of the scope.On top of this, work on the final 
presentation has begun. CLI is fully functional and can implement the 
commands needed to run the methods in the API. I wrote some stuff on 
targets not met but wasn't aware to implement those until after our 
meeting. Will work on those this week. CLI has the functionality to 
implement the methods in the API and connect with wpa\_supplicant. 
The API implementation has taken a few big steps in that the layour of the
program is fully fucntioning, and user interactions can be taken and dealt
with. While the TUI BSD Makefile has been implemented, and the API call for
Available networks is not implemented to gain and display possible network
connections.

\textbf{Accomplishments}
\begin{itemize}
  \item CLI has more common commands such as 'connect', 'disconnect', etc. 
\end{itemize}

\textbf{Targets Not Met:}
\begin{itemize}
  \item CLI should be able to determine the current connection. 
  \item CLI should be able to determine if a network is an EAP network. 
  \item API implementation not quite at 50 percent but very close 
\end{itemize}

\textbf{New Expectations:}
API should at the very least be able 
to display Available networks and have the user be able to select a network,
possible implementation of network info on sub window is also very attainable.

\section{Git Branch Report}

\newpage
\section{Individual Progress}

\textbf{Kevin: 7 hours, 45 minutes}
\begin{itemize}
  \item implemented sub window for network information display
  \item Created and implemented BSD Makefile almost fully
  \item Implemented API functions to get Available networks
  \item Moved all of the TUI\_test branch into master
\end{itemize}

\textbf{Dylan:} 4 hours
\begin{itemize}
  \item Marginal progress on GUI
  \item Started prep for our presentation
\end{itemize}

\textbf{Stephen: 4 hours, 4 minutes}
\begin{itemize}
  \item CLI is fully functional and can run the methods in the API 
  \item CLI was reorganized to be more suitable by the requirements and has 
	common commands such as 'connect', 'disconnect', 'forget', 'add', 'edit' 
	and 'configure'.
\end{itemize}

\end{document}
