\documentclass[11pt]{article}
\setlength{\parindent}{0em}
\usepackage[margin=1in]{geometry}

\begin{document}

\begin{center}
  \textbf{\Large Milestone \#7}\\\large NetBSD Wifi Browser Project 2022\\
  Dylan Roy, Stephen Loudiana, Kevin McGrane
\end{center}

\section{General Progress Report}
Progress within Surf was fairly minimal this milestone. Being that it
is functinally complete, little tasks are being performed to improve
it in small ways. Along with this, the Makefiles were converted to BSDMake. 
Progress for CLI mostly involved thoroughly taking the time to understand 
the skeleton code and implement the remaining CLI methods. Some research on 
getopt_long and how I might implement it. Cannot test CLI interface on my 
computer through WWU Linux shell. Currently looking for a solution to this. 
TUI implementation is well under way, skeleton and layout of TUI is complete 
and API is beiginning to be implemented. Most of the current work is looking
at the curses man pages to figure out what functions are needed when retrieving 
data from the API and printing it, and also when retrieving input from the user
and sending it to the API.

\textbf{Accomplishments}
\begin{itemize}
  \item Surf listing output has been improved 
  \item Makefiles converted to BSDMake
  \item All API methods implemented in CLI 
  \item Have TUI be able to be interacted with
\end{itemize}

\textbf{Targets Not Met:}
\begin{itemize}
  \item Cannot test CLI interface on Stephen's computer 
  \item TUI implementation not yet at 50 percent implemented
\end{itemize}


\section{Git Branch Report}
A branch, \texttt{TUI\_test} was made to begin implementation of the TUI.

\newpage
\section{Individual Progress}

\textbf{Kevin:} 7 hours
\begin{itemize}
  \item created seperate TUI branch as not to mess up the API and CLI when they are testing
  \item uploaded some of the TUI implementation to test branch (more needs to be Added)
  \item worked with window creation and implementation of TUI display for user interface
  \item worked with curses man pages to asses what functions are needed when giving and getting info from the API
\end{itemize}

\textbf{Dylan:} 4 hours, 5 minutes
\begin{itemize}
  \item Improve the output for Surf's listing functions
  \item Moved the testing files for Surf into the dedicated test directory
  \item Added a testing script to automate Surf testing
  \item Converted all of Surf's Makefiles into BSDMake
  \item Modified Surf's error output to only print when \texttt{DEBUG} flag set
    at compile time $\rightarrow$ might send to a log alternatively
\end{itemize}

\textbf{Stephen:} 4 hours, 0 minutes 
\begin{itemize}
  \item All API methods for the CLI have been implemented 
  \item Thoroughly took the time to go through the code, did some research on getopt_long
	and how to implement it
  \item Cannot test CLI interface on my home console, will need to find solution. I'm not 
	sure why but I cannot connect to wpa_supplicant through WWU Linux shell. Currently 
	looking for a solution to this. 
\end{itemize}

\end{document}
